### 2019-03-10 papers/journal/encoding.tex
removed the recahability disccusion as a seperate subsection
moved section 6.3 and 6.4 to subsection of the 6.2

\subsection{The key difference in the reachability encoding}
The key improvement of the SMT tool over the BMC is the
encoding of reachability.
% which was done using an enumeration of paths.
%
In the BMC tool, reachability is encoded by enumerating all the possible paths using nondeterminism.
%
This encoding is non-optimal in the sense that in the worst case an exponential number of paths needs to be explored.
%
Whereas in the SMT tool, reachability is encoded in two different
ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
%
The reachability is recursively defined in~\eqref{eq:drop3} and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
only the solutions that captures the evidence of unreachability.
%
On the other hand,
we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1},
which needs relatively more auxiliary variables.
%
This is because constraint~\eqref{eq:reach2} has only positive
occurrences of the reachability variables and if we had defined
$r$s in ~\eqref{eq:reach1} without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

@@

\subsection{BMC and SMT problems for different variants}
%\ankit{Bring model variant table here}

>>>>

\subsubsection{The key difference in the reachability encoding}:
The key improvement of the SMT tool over the BMC is the
encoding of reachability.
% which was done using an enumeration of paths.
%
In the BMC tool, reachability is encoded by enumerating all the possible paths using nondeterminism.
%
This encoding is non-optimal in the sense that in the worst case an exponential number of paths needs to be explored.
%
Whereas in the SMT tool, reachability is encoded in two different
ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
%
The reachability is recursively defined in~\eqref{eq:drop3} and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
only the solutions that captures the evidence of unreachability.
%
On the other hand,
we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1},
which needs relatively more auxiliary variables.
%
This is because constraint~\eqref{eq:reach2} has only positive
occurrences of the reachability variables and if we had defined
$r$s in ~\eqref{eq:reach1} without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

@@

\subsubsection{BMC and SMT problems for different variants}
%\ankit{Bring model variant table here}
